---
title: "Thematic analysis"
output:
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(dplyr)

df_theme <- readxl::read_xlsx("data/Data extraction vaccine equity.xlsx",
                        sheet = "Aims&Objectives") %>%
   mutate(covidence_id = as.numeric(covidence_id))

df_names <- read.csv("cleaned_data.csv", stringsAsFactors = FALSE)

df_names <- df_names %>% 
  select(covidence_id, first_author_surname, year_of_article) %>% 
  distinct() %>%
  mutate(covidence_id = as.numeric(covidence_id))

df_theme <- df_theme %>% left_join(df_names, by = "covidence_id")
```

# Introduction

This document takes the theme notes from the data collection spreadsheets and pastes them together with the reference. In many places, this is direct quotes so will need to be completely rewritten. The hope is that this document is an easy summary to read.

# Role of equity in the impact of vaccination in LMICs

## Definition

How does inequity/ heterogeneity or inequality change the *influence* of vaccination ie. if you had the same coverage of a vaccine in two populations, would the affects be different? An example of this is measles where the CFR is a function of socioeconomic factors so vaccination will prevent more deaths in a population where the CFR is higher.

## Information collected

```{r}
out <- df_theme %>%
  filter(!is.na(`role of equity on the impact of vaccination in LMICs`)) %>%
  mutate(out_text = paste0(`role of equity on the impact of vaccination in LMICs`,
                           " [",
                           first_author_surname,
                           " ",
                           year_of_article,
                           "].")) 
out <- paste0(out$out_text, collapse = " ")

```

`r paste(out)`

## List of studies including information

```{r}
out <- df_theme %>%
  filter(!is.na(`role of equity on the impact of vaccination in LMICs`)) %>% 
  arrange(first_author_surname) %>%
  mutate(out_text = paste0("[",
                           first_author_surname,
                           " ",
                           year_of_article,
                           "], ")) 

out <- paste0(out$out_text, collapse = " ")
```

`r paste(out)`

# How vaccine access varies geographically

## Definition

How does coverage or access to immunisation change over space or geography including are there divisions between urban and rural populations.

## Information collected

```{r}
out <- df_theme %>%
  filter(!is.na(`how vaccine access varies geographically`)) %>%
  mutate(out_text = paste0(`how vaccine access varies geographically`,
                           " [",
                           first_author_surname,
                           " ",
                           year_of_article,
                           "].")) 
out <- paste0(out$out_text, collapse = " ")

```

`r paste(out)`

## List of studies including information

```{r}
out <- df_theme %>%
  filter(!is.na(`how vaccine access varies geographically`)) %>% 
  arrange(first_author_surname) %>%
  mutate(out_text = paste0("[",
                           first_author_surname,
                           " ",
                           year_of_article,
                           "], ")) 

out <- paste0(out$out_text, collapse = " ")
```

`r paste(out)`

# How vaccine access varies demographically

## Definition

What demographic factors affect vaccine coverage or access? For example is there a difference seen by age or gender?

## Information collected

```{r}
out <- df_theme %>%
  filter(!is.na(`how vaccine access varies demographically`)) %>%
  mutate(out_text = paste0(`how vaccine access varies demographically`,
                           " [",
                           first_author_surname,
                           " ",
                           year_of_article,
                           "].")) 
out <- paste0(out$out_text, collapse = " ")

```

`r paste(out)`

## List of studies including information

```{r}
out <- df_theme %>%
  filter(!is.na(`how vaccine access varies demographically`)) %>% 
  arrange(first_author_surname) %>%
  mutate(out_text = paste0("[",
                           first_author_surname,
                           " ",
                           year_of_article,
                           "], ")) 

out <- paste0(out$out_text, collapse = " ")
```

`r paste(out)`

# How vaccine access varies socioeconomically

## Definition

What socioeconomic factors affect vaccine coverage or access? For example is there a difference seen by wealth quintile or educational attainment?

## Information collected

```{r}
out <- df_theme %>%
  filter(!is.na(`how vaccine access varies socioeconomically.`)) %>%
  mutate(out_text = paste0(`how vaccine access varies socioeconomically.`,
                           " [",
                           first_author_surname,
                           " ",
                           year_of_article,
                           "].")) 
out <- paste0(out$out_text, collapse = " ")

```

`r paste(out)`

## List of studies including information

```{r}
out <- df_theme %>%
  filter(!is.na(`how vaccine access varies socioeconomically.`)) %>% 
  arrange(first_author_surname) %>%
  mutate(out_text = paste0("[",
                           first_author_surname,
                           " ",
                           year_of_article,
                           "], ")) 

out <- paste0(out$out_text, collapse = " ")
```

`r paste(out)`

# Heterogeneity in vaccination access in LMICs

## Definition

How does access or coverage change across LMICs - is there a measure of the variation subnationally and or internationally?

## Information collected

```{r}
out <- df_theme %>%
  filter(!is.na(`heterogeneity in vaccination access in LMICs`)) %>%
  mutate(out_text = paste0(`heterogeneity in vaccination access in LMICs`,
                           " [",
                           first_author_surname,
                           " ",
                           year_of_article,
                           "].")) 
out <- paste0(out$out_text, collapse = " ")

```

`r paste(out)`

## List of studies including information

```{r}
out <- df_theme %>%
  filter(!is.na(`heterogeneity in vaccination access in LMICs`)) %>% 
  arrange(first_author_surname) %>%
  mutate(out_text = paste0("[",
                           first_author_surname,
                           " ",
                           year_of_article,
                           "], ")) 

out <- paste0(out$out_text, collapse = " ")
```

`r paste(out)`